The LHC as a Neutrino-Ion Collider

### 2023-09-27 journal_sub/sec-dis-pseudodata.tex
Add epjc typeset version

The double-differential cross-section for neutrino-nucleus charged-current scattering,
see~\cite{Candido:2023utz} and references therein,
can be expressed in terms of three
independent structure functions $F_2^{\nu A}$, $xF_3^{\nu A}$
and $F_L^{\nu A}$:
\be
\label{eq:neutrino_DIS_xsec_FL}
\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\nu A}_2(x,Q^2) - y^2F^{\nu A}_L(x,Q^2) +Y_- xF^{\nu A}_3(x,Q^2)\rc  \, ,
\ee
where $Y_\pm = 1 \pm (1-y)^2$ and with a counterpart expression for anti-neutrino scattering,
\be
\label{eq:antineutrino_DIS_xsec_FL}
\frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\bar{\nu} A}_2(x,Q^2) - y^2F^{\bar{\nu} A}_L(x,Q^2) -Y_- xF^{\bar{\nu} A}_3(x,Q^2)\rc  \, ,
\ee
with $s=2m_N E_\nu$ being the neutrino-nucleon centre-of-mass energy squared, $m_N$ the nucleon mass,
$E_\nu$ the incoming neutrino energy,
and $y=Q^2/(2x m_n E_{\nu})$ the inelasticity.
%
In the case of tau-neutrino scattering, tau-lepton mass effects
may be relevant and Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) receive additional contributions
from the $F_4$ and $F_5$ structure functions.
%
We neglect these effects, since here we focus on electron and muon neutrino scattering.

Structure functions depend on both $x$ and $Q^2$, while the differential
cross-section depends also on the neutrino energy $E_\nu$, or alternatively
on the inelasticity $y$.
%
Further, structure functions $F^{\nu A}_i(x,Q^2)$ and $F^{\bar{\nu} A}_i(x,Q^2)$ depend on the nuclear target $A$ entering neutrino scattering through the
nuclear modifications of the free-nucleon PDFs.
%
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) are valid provided
the hadronic 
invariant mass $W$  is above the resonance production threshold,
\be
\label{eq:W2_invmass}
W^2 = \lp m_N^2 + Q^2 \frac{(1-x)}{x} \rp \gsim \lp 2\,{\rm GeV} \rp^2\, .
\ee
In addition, here we  restrict ourselves to the DIS region with perturbative momentum
transfers $Q^2 \gsim 2$ GeV$^2$, such that the structure functions can be decomposed as
\be
\label{eq:sfs_pqcd}
 F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g}\int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \quad i = 2,3,L \, .
 \ee
%
 expressed
 in terms of a convolution of partonic scattering cross-sections  $C_{i,j}^{\nu N}(x,\alpha_s)$ and
of process-independent PDFs $f^{(A)}_j\lp x,Q^2\rp$.
%
A similar expression holds for charm production~\cite{Faura:2020oom}, which requires
accounting also for charm mass effects~\cite{Gao:2017kkx}.
%
Here the theory pipeline adopted
to evaluate neutrino structure functions using Eq.~(\ref{eq:sfs_pqcd}) is provided by 
{\sc\small EKO}~\cite{Candido:2022tld}
and {\sc\small YADISM}~\cite{yadism,Candido:2023utz}
interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss}
for the generation of fast interpolation grids.

Different neutrino structure functions provide complementary sensitivity
 to the partonic flavour decompositions of nucleons.
 %
 To illustrate this feature, consider a leading order  calculation
 for a proton target with $n_f=4$ active quark flavours,
a diagonal CKM matrix, and no heavy quark mass effects.
 %
 The resulting $F_2^{\nu p}$ and $xF_3^{\nu p}$ structure functions read
 \bea
 F_2^{\nu p}(x,Q^2) &=& 2x\lp f_{\bar{u}} + f_{d} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
 F_2^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u + f_{\bar{d}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs_proton} \\
 xF_3^{\nu p}(x,Q^2) &=& 2x\lp -f_{\bar{u}} + f_d +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
 xF_3^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u - f_{\bar{d}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, . \nonumber
 \eea
 The corresponding expressions for a neutron target are obtained from isospin symmetry
 \bea
 F_2^{\nu n}(x,Q^2) &=& 2x\lp f_{\bar{d}} + f_{u} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
 F_2^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d + f_{\bar{u}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:antineutrinoSFs_neutron} \\
 xF_3^{\nu n}(x,Q^2) &=& 2x\lp -f_{\bar{d}} + f_u +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
 xF_3^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d - f_{\bar{u}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, , \nonumber
 \eea
 while for an isoscalar, free-nucleon target denoted by $N$ one has
 \bea
 F_2^{\nu N}(x,Q^2) &=& 2x\lp f_{u^+} + f_{d^+} + 2f_s + 2f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
 F_2^{\bar{\nu} N}(x,Q^2) &=& 2x\lp f_{u^+} + f_{d^+} + 2f_{\bar{s}} + 2f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs_isoscalar} \\
 xF_3^{\nu N}(x,Q^2) &=& 2x\lp f_{u^-} + f_{d^-} +2f_s - 2f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
 xF_3^{\bar{\nu} N}(x,Q^2) &=& 2x\lp   f_{u^-} + f_{d^-}-2f_{\bar{s}} +2 f_{c}\rp(x,Q^2) \, , \nonumber
 \eea
 in terms of the valence and sea PDF combinations defined by
 \be
 f_{q^+} (x,Q^2)\equiv \lp f_{q}+f_{\bar{q}}\rp(x,Q^2) \, , \qquad
 f_{q^-} (x,Q^2)\equiv \lp f_{q}- f_{\bar{q}}\rp(x,Q^2) \, .
 \ee
 We note that, even for isoscalar targets, separate measurements
 for neutrinos and antineutrinos will not be equivalent, since in general
 the strange and charm sea asymmetries $f_{s^-}$ and
 $f_{c^-}$ are not expected to vanish.

@@

 It is also illustrative to compare the PDF dependence of neutrino structure functions
 at LO with that of their counterparts for neutral-current
 scattering with a charged lepton projectile.
 %
 Within the same assumptions, for energies below
 the $Z$-boson mass, $Q^2 \ll m_Z^2$, the corresponding
decomposition is \bea
 F_2^{\ell p}(x,Q^2) &=& x\lp \frac{4}{9}\lc f_{u^+} + f_{c^+}\rc
 + \frac{1}{9}\lc f_{d^+} + f_{s^+}\rc\rp(x,Q^2) \, , \nonumber  \\
 F_2^{\ell n}(x,Q^2) &=& x\lp \frac{4}{9}\lc f_{d^+} + f_{c^+}\rc
 + \frac{1}{9}\lc f_{u^+} + f_{s^+}\rc\rp(x,Q^2) \, ,\label{eq:NC_chargedlepton}   \\
 F_2^{\ell N}(x,Q^2) &=& x\lp \frac{5}{18}\lc f_{u^+} + f_{d^+}\rc
 + \frac{1}{9} f_{s^+} + \frac{4}{9} f_{c^+} \rp(x,Q^2) \, , \nonumber  
 \eea
 with $xF_3$ being negligible in this region.
 %
 Comparing Eqns.~(\ref{eq:neutrinoSFs_proton})--(\ref{eq:neutrinoSFs_isoscalar})
 with Eq.~(\ref{eq:NC_chargedlepton}) showcases the complementarity between
 neutrino and charged-lepton DIS in terms of sensitivity
 to different flavour PDF combinations.
 %
 This implies that the best sensitivity on the quark
  flavour separation in the nucleon
 would be provided by combining neutrino DIS from the
 LHC far-forward experiments with measurements on charged-lepton
 DIS at the EIC.

@@

For each of the LHC far-forward neutrino detectors
described in Table~\ref{tab:FPF_experiments}, we generate
projections for the expected DIS structure function
measurements as follows.
%
We want to evaluate the number of reconstructed charged-current neutrino interaction
events taking place in the fiducial volume of the detector when divided into bins of Bjorken-$x$,
momentum transfer $Q^2$, and neutrino energy $E_\nu$, that is,
\be
\label{eq:event_yields}
N_{\nu_e,{\rm ev}}^{(i)}\lp \nu_e ; E_{{\rm min}}^{(i)} \le E_\nu \le E_{{\rm max}}^{(i)} ;\,
x_{{\rm min}}^{(i)} \le x \le x_{{\rm max}}^{(i)} ;\, Q_{{\rm min}}^{2(i)} \le Q^2 \le Q_{{\rm max}}^{2(i)}\rp
\, ,\quad i=1,\ldots, N_{\rm bin} \, ,
\ee
for electron neutrinos and for each of the bins composing the measurement, and with similar
expressions applying for muon neutrinos and antineutrinos.
%
These event yields determine the statistical
precision associated to a measurement of the double-differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Subsequently, we account for the expected reconstruction performance of the detector
in order to estimate the systematic uncertainties associated to these event yields.
%
For simplicity, in this initial study we consider a single bin in energy
and choose log-spaced bins in $x$ and $Q^2$; the eventual optimisation
of the binning selection is left for future work.

In this calculation, we adopt the neutrino fluxes evaluated in~\cite{Kling:2021gos} and used
for the FPF simulations presented in~\cite{Feng:2022inv}.
%
The bin-by-bin integrated event yields in Eq.~(\ref{eq:event_yields}) are
obtained by convoluting the incoming neutrino fluxes, for a given acceptance
of the target detector, with the corresponding neutrino differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Binned event yields are evaluated using
\begin{equation}
  \label{eq:event_yields_calculation}
   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,
\end{equation}
with $n_T$ is the nucleon density of the target detector material, $L_T$ its
length, and ${\cal A}(x,Q^2,E_{\nu})$ is an global acceptance factor which takes the form of a
step function and accounts for the experimental acceptances
in $E_\ell$, $\theta_\ell$, and $E_h$
listed in Table~\ref{tab:FPF_experiments}.

@@

Eq.~(\ref{eq:event_yields_calculation}) can be generalised to charm-production events, with
the only difference being that now the neutrino scattering cross-section is restricted
to those processes leading to final-state charm quarks.
%
Assuming that charm quarks can be directly tagged by the detector one has
\be
\label{eq:event_yields_charm}
  N_{\rm ev,c}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma^{\nu N \to \ell + c+X}(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,
  \ee
  with the charm production cross-sections discussed in~\cite{Faura:2020oom}
  and references therein.
  %
   Here we neglect efficiency and acceptance effects associated to $D$-meson
 tagging, which can only be properly estimated by means
 of a full detector simulation.
 %
 The acceptance correction ${\cal A}(x,Q^2,E_{\nu})$ in Eq.~(\ref{eq:event_yields_charm})
 applies only to the charged leptons and hence is the same as in
 the inclusive case.

@@

%-----------------------------------------------------------------------
\begin{figure}[t]
    \centering
    \includegraphics[width=0.495\textwidth]{plots/FPF-FASERv.pdf}
    \includegraphics[width=0.495\textwidth]{plots/FPF-FASERv2.pdf}
    \includegraphics[width=0.495\textwidth]{plots/FPF-AdvSND.pdf}
    \includegraphics[width=0.495\textwidth]{plots/FPF-FLArE100.pdf}
    \caption{
    	\small The event yields per bin $N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}), for 
    	muon-neutrino scattering at the FASER$\nu$, FASER$\nu$2, AdvSND, and FLArE100  experiments.
        %
   		Selected events are restricted to the DIS region Eq.~(\ref{eq:DISconditions})
   		and only bins with $\ge 100$ events are retained except for FASER$\nu$ in which
   		bins with $\ge 10$ events are kept.
		%
		Adding up the bins in each of the panels results into the numbers listed in
		Table~\ref{tab:integrated_rates}.}
    \label{fig:fasernu2_muon}
\end{figure}
%-----------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width = 0.80\textwidth]{plots/KIN_DIS_FPF.pdf}
    \caption{
      The kinematic coverage in the $(x,Q^2)$ plane of muon-neutrino scattering
      at the FASER$\nu$, FASER$\nu$2, FLArE10(100), and AdvSND experiments, see also Fig.~\ref{fig:fasernu2_muon},
      compared to that of electron-ion collisions at the EIC
      as well as to the coverage of existing neutrino
      fixed-target DIS measurements.
    }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
    \centering
    \includegraphics[width = \textwidth]{plots/Event_Rate_FASERv2.pdf}
    \caption{Same as Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2
      now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$
      for both the neutrino and antineutrinos.
      %
      In addition to the event yield values, we also show the error bars corresponding to
      statistical errors only (left), systematic errors only (middle), and the
      sum in quadrature of the two (right panel).
      %
      The bars in the horizontal direction indicate the width of the adopted $x$-bins.
      }
    \label{fig:error_plot_FASERv2_14}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The double-differential cross-section for neutrino-nucleus charged-current scattering,
see~\cite{Candido:2023utz} and references therein,
can be expressed in terms of three
independent structure functions $F_2^{\nu A}$, $xF_3^{\nu A}$
and $F_L^{\nu A}$:
\begin{align}
	\label{eq:neutrino_DIS_xsec_FL}
	&\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\\ 
	& \lc Y_+F^{\nu A}_2(x,Q^2) - y^2F^{\nu A}_L(x,Q^2) +Y_- xF^{\nu A}_3(x,Q^2)\rc, \nonumber
\end{align}
where $Y_\pm = 1 \pm (1-y)^2$ and with a counterpart expression for anti-neutrino scattering,
\begin{align}
	\label{eq:antineutrino_DIS_xsec_FL}
	&\frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2} \\
	& \lc Y_+F^{\bar{\nu} A}_2(x,Q^2) - y^2F^{\bar{\nu} A}_L(x,Q^2) -Y_- xF^{\bar{\nu} A}_3(x,Q^2)\rc,
	\nonumber
\end{align}
with $s=2m_N E_\nu$ being the neutrino-nucleon centre-of-mass energy squared, $m_N$ the nucleon mass,
$E_\nu$ the incoming neutrino energy,
and $y=Q^2/(2x m_n E_{\nu})$ the inelasticity.
%
In the case of tau-neutrino scattering, tau-lepton mass effects
may be relevant and Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) receive additional contributions
from the $F_4$ and $F_5$ structure functions.
%
We neglect these effects, since here we focus on electron and muon neutrino scattering.

Structure functions depend on both $x$ and $Q^2$, while the differential
cross-section depends also on the neutrino energy $E_\nu$, or alternatively
on the inelasticity $y$.
%
Further, structure functions $F^{\nu A}_i(x,Q^2)$ and $F^{\bar{\nu} A}_i(x,Q^2)$ depend on the nuclear target $A$ entering neutrino scattering through the
nuclear modifications of the free-nucleon PDFs.
%
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) are valid provided
the hadronic 
invariant mass $W$  is above the resonance production threshold,
\be
\label{eq:W2_invmass}
W^2 = \lp m_N^2 + Q^2 \frac{(1-x)}{x} \rp \gsim \lp 2\,{\rm GeV} \rp^2\, .
\ee
In addition, here we  restrict ourselves to the DIS region with perturbative momentum
transfers $Q^2 \gsim 2$ GeV$^2$, such that the structure functions can be decomposed as
\begin{align}
	\label{eq:sfs_pqcd}
	F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g} & \int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}
	(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \nonumber \\
	& \text{ with } \quad i = 2,3,L \, ,
\end{align}
%
 expressed
 in terms of a convolution of partonic scattering cross-sections  $C_{i,j}^{\nu N}(x,\alpha_s)$ and
of process-independent PDFs $f^{(A)}_j\lp x,Q^2\rp$.
%
A similar expression holds for charm production~\cite{Faura:2020oom}, which requires
accounting also for charm mass effects~\cite{Gao:2017kkx}.
%
Here the theory pipeline adopted
to evaluate neutrino structure functions using Eq.~(\ref{eq:sfs_pqcd}) is provided by 
{\sc\small EKO}~\cite{Candido:2022tld}
and {\sc\small YADISM}~\cite{yadism,Candido:2023utz}
interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss}
for the generation of fast interpolation grids.

Different neutrino structure functions provide complementary sensitivity
 to the partonic flavour decompositions of nucleons.
 %
 To illustrate this feature, consider a leading order  calculation
 for a proton target with $n_f=4$ active quark flavours,
a diagonal CKM matrix, and no heavy quark mass effects.
 %
 The resulting $F_2^{\nu p}$ and $xF_3^{\nu p}$ structure functions read
\begin{align}
	 F_2^{\nu p}(x,Q^2) &= 2x\lp f_{\bar{u}} + f_{d} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
	F_2^{\bar{\nu} p}(x,Q^2) &= 2x\lp f_u + f_{\bar{d}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs_proton} \\
	xF_3^{\nu p}(x,Q^2) &= 2x\lp -f_{\bar{u}} + f_d +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
	xF_3^{\bar{\nu} p}(x,Q^2) &= 2x\lp f_u - f_{\bar{d}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, . \nonumber
\end{align}
 The corresponding expressions for a neutron target are obtained from isospin symmetry
 \begin{align}
 	 F_2^{\nu n}(x,Q^2) &= 2x\lp f_{\bar{d}} + f_{u} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
 	F_2^{\bar{\nu} n}(x,Q^2) &= 2x\lp f_d + f_{\bar{u}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:antineutrinoSFs_neutron} \\
 	xF_3^{\nu n}(x,Q^2) &= 2x\lp -f_{\bar{d}} + f_u +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
 	xF_3^{\bar{\nu} n}(x,Q^2) &= 2x\lp f_d - f_{\bar{u}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, , \nonumber
 \end{align}
 while for an isoscalar, free-nucleon target denoted by $N$ one has
 \begin{align}
 	\noindent
 	&F_2^{\nu N}(x,Q^2)= 2x\lp f_{u^+} + f_{d^+} + 2f_s + 2f_{\bar{c}} \rp(x,Q^2), \nonumber  \\
 	&F_2^{\bar{\nu} N}(x,Q^2)= 2x\lp f_{u^+} + f_{d^+} + 2f_{\bar{s}} + 2f_c \rp(x,Q^2), \label{eq:neutrinoSFs_isoscalar} \\
 	&xF_3^{\nu N}(x,Q^2)= 2x\lp f_{u^-} + f_{d^-} +2f_s - 2f_{\bar{c}}\rp(x,Q^2), \nonumber\\
 	&xF_3^{\bar{\nu} N}(x,Q^2)= 2x\lp   f_{u^-} + f_{d^-}-2f_{\bar{s}} +2 f_{c}\rp(x,Q^2), \nonumber \qquad
 \end{align}
 in terms of the valence and sea PDF combinations defined by the following relations
\begin{align}
	 f_{q^+} (x,Q^2) &\equiv \lp f_{q}+f_{\bar{q}}\rp(x,Q^2) \, , \nonumber \\
	f_{q^-} (x,Q^2) &\equiv \lp f_{q}- f_{\bar{q}}\rp(x,Q^2) \, .
\end{align}
 We note that, even for isoscalar targets, separate measurements
 for neutrinos and antineutrinos will not be equivalent, since in general
 the strange and charm sea asymmetries $f_{s^-}$ and
 $f_{c^-}$ are not expected to vanish.

@@

 It is also illustrative to compare the PDF dependence of neutrino structure functions
 at LO with that of their counterparts for neutral-current
 scattering with a charged lepton projectile.
 %
 Within the same assumptions, for energies below
 the $Z$-boson mass, $Q^2 \ll m_Z^2$, the corresponding
decomposition is
\begin{align}
	 F_2^{\ell p}(x,Q^2) &= x\lp \frac{4}{9}\lc f_{u^+} + f_{c^+}\rc
	+ \frac{1}{9}\lc f_{d^+} + f_{s^+}\rc\rp(x,Q^2) \, , \nonumber  \\
	F_2^{\ell n}(x,Q^2) &= x\lp \frac{4}{9}\lc f_{d^+} + f_{c^+}\rc
	+ \frac{1}{9}\lc f_{u^+} + f_{s^+}\rc\rp(x,Q^2) \, , \nonumber   \\
	F_2^{\ell N}(x,Q^2) &= x\lp \frac{5}{18}\lc f_{u^+} + f_{d^+}\rc
	+ \frac{1}{9} f_{s^+} + \frac{4}{9} f_{c^+} \rp(x,Q^2) \, , \label{eq:NC_chargedlepton} 
\end{align}
 with $xF_3$ being negligible in this region.
 %
 Comparing Eqns. (\ref{eq:neutrinoSFs_proton})--(\ref{eq:neutrinoSFs_isoscalar})
 with Eq.~(\ref{eq:NC_chargedlepton}) showcases the complementarity between
 neutrino and charged-lepton DIS in terms of sensitivity
 to different flavour PDF combinations.
 %
 This implies that the best sensitivity on the quark
  flavour separation in the nucleon
 would be provided by combining neutrino DIS from the
 LHC far-forward experiments with measurements on charged-lepton
 DIS at the EIC.

@@

For each of the LHC far-forward neutrino detectors
described in Table~\ref{tab:FPF_experiments}, we generate
projections for the expected DIS structure function
measurements as follows.
%
We want to evaluate the number of reconstructed charged-current neutrino interaction
events taking place in the fiducial volume of the detector when divided into bins of Bjorken-$x$,
momentum transfer $Q^2$, and neutrino energy $E_\nu$, that is,
\begin{align}
	\label{eq:event_yields}
	N_{\nu_e,{\rm ev}}^{(i)}\lp \nu_e ;  E_\nu; x; Q^2\rp
	\, ,\quad i=1,\ldots, N_{\rm bin},
\end{align}
with
\allowdisplaybreaks
\begin{align}
	E_{{\rm min}}^{(i)} &\le E_\nu \le E_{{\rm max}}^{(i)}, \nonumber \\
	x_{{\rm min}}^{(i)} &\le x \le x_{{\rm max}}^{(i)} , \nonumber \\
	Q_{{\rm min}}^{2(i)} & \le Q^2 \le Q_{{\rm max}}^{2(i)}, \nonumber
\end{align}
\allowdisplaybreaks
for electron neutrinos and for each of the bins composing the measurement, and with similar
expressions applying for muon neutrinos and antineutrinos.
%
These event yields determine the statistical
precision associated to a measurement of the double-differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Subsequently, we account for the expected reconstruction performance of the detector
in order to estimate the systematic uncertainties associated to these event yields.
%
For simplicity, in this initial study we consider a single bin in energy
and choose log-spaced bins in $x$ and $Q^2$; the eventual optimisation
of the binning selection is left for future work.

In this calculation, we adopt the neutrino fluxes evaluated in~\cite{Kling:2021gos} and used
for the FPF simulations presented in~\cite{Feng:2022inv}.
%
The bin-by-bin integrated event yields in Eq.~(\ref{eq:event_yields}) are
obtained by convoluting the incoming neutrino fluxes, for a given acceptance
of the target detector, with the corresponding neutrino differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Binned event yields are evaluated using
\begin{align}
  \label{eq:event_yields_calculation}
   N_{\rm ev}^{(i)} =& n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}} \\ 
   &\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, , \nonumber
\end{align}
with $n_T$ is the nucleon density of the target detector material, $L_T$ its
length, and ${\cal A}(x,Q^2,E_{\nu})$ is an global acceptance factor which takes the form of a
step function and accounts for the experimental acceptances
in $E_\ell$, $\theta_\ell$, and $E_h$
listed in Table~\ref{tab:FPF_experiments}.

@@

Eq.~(\ref{eq:event_yields_calculation}) can be generalised to charm-production events, with
the only difference being that now the neutrino scattering cross-section is restricted
to those processes leading to final-state charm quarks.
%
Assuming that charm quarks can be directly tagged by the detector one has
\begin{align}
	\label{eq:event_yields_charm}
	&N_{\rm ev,c}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}
	\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}} \\
	&\left(\frac{d^2\sigma^{\nu N \to \ell + c+X}(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, , 
	\nonumber
\end{align}
with the charm production cross-sections discussed in~\cite{Faura:2020oom}
and references therein.
%
Here we neglect efficiency and acceptance effects associated to $D$-meson
tagging, which can only be properly estimated by means
of a full detector simulation.
%
The acceptance correction ${\cal A}(x,Q^2,E_{\nu})$ in Eq.~(\ref{eq:event_yields_charm})
applies only to the charged leptons and hence is the same as in
the inclusive case.

@@

%-----------------------------------------------------------------------
\begin{figure*}[t]
    \centering
    \includegraphics[width=0.495\textwidth]{plots/FPF-FASERv.pdf}
    \includegraphics[width=0.495\textwidth]{plots/FPF-FASERv2.pdf}
    \includegraphics[width=0.495\textwidth]{plots/FPF-AdvSND.pdf}
    \includegraphics[width=0.495\textwidth]{plots/FPF-FLArE100.pdf}
    \caption{
    	\small The event yields per bin $N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}), for 
    	muon-neutrino scattering at the FASER$\nu$, FASER$\nu$2, AdvSND, and FLArE100  experiments.
        %
   		Selected events are restricted to the DIS region Eq.~(\ref{eq:DISconditions})
   		and only bins with $\ge 100$ events are retained except for FASER$\nu$ in which
   		bins with $\ge 10$ events are kept.
		%
		Adding up the bins in each of the panels results into the numbers listed in
		Table~\ref{tab:integrated_rates}.}
    \label{fig:fasernu2_muon}
\end{figure*}
%-----------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
    \centering
    \includegraphics[width = 0.80\textwidth]{plots/KIN_DIS_FPF.pdf}
    \caption{
      The kinematic coverage in the $(x,Q^2)$ plane of muon-neutrino scattering
      at the FASER$\nu$, FASER$\nu$2, FLArE10(100), and AdvSND experiments, see also Fig.~\ref{fig:fasernu2_muon},
      compared to that of electron-ion collisions at the EIC
      as well as to the coverage of existing neutrino
      fixed-target DIS measurements.
    }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[h]
    \centering
    \includegraphics[width = \textwidth]{plots/Event_Rate_FASERv2.pdf}
    \caption{Same as Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2
      now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$
      for both the neutrino and antineutrinos.
      %
      In addition to the event yield values, we also show the error bars corresponding to
      statistical errors only (left), systematic errors only (middle), and the
      sum in quadrature of the two (right panel).
      %
      The bars in the horizontal direction indicate the width of the adopted $x$-bins.
      }
    \label{fig:error_plot_FASERv2_14}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-09-27 journal_sub/sec-summary.tex
Add epjc typeset version

Together with this paper, we 
make public in Zenodo
the corresponding {\sc\small LHAPDF} grids~\cite{Buckley:2014ana}
for the PDF4LHC21 and NNPDF4.0 fits including FPF data.
%
We also release
the generated neutrino structure function pseudo-data
and the corresponding theory
calculations, for the different scenarios considered in this work.
%
These projections for neutrino structure functions
should be of relevance for a broad range of
applications related to forward
neutrino scattering at the LHC, from tests
of lepton flavour university at the TeV scale
in the neutrino sector to probes of anomalous neutrino
interactions and searches for sterile neutrinos
distorting  oscillation patterns.

>>>>

Together with this paper, we 
make public in Zenodo~\cite{cruz_martinez_juan_2023_8355209}
the corresponding {\sc\small LHAPDF} grids~\cite{Buckley:2014ana}
for the PDF4LHC21 and NNPDF4.0 fits including FPF data.
%
We also release
the generated neutrino structure function pseudo-data
and the corresponding theory
calculations, for the different scenarios considered in this work.
%
These projections for neutrino structure functions
should be of relevance for a broad range of
applications related to forward
neutrino scattering at the LHC, from tests
of lepton flavour university at the TeV scale
in the neutrino sector to probes of anomalous neutrino
interactions and searches for sterile neutrinos
distorting  oscillation patterns.
